Multi-level modeling with Openflexo/\FML

### 2022-03-11 5-analysis.tex
remove comments concerning the figures: we discussed the representation during the writing of the article and we agreed on the current version. Reviewers did not seem to be lost and the article has been accepted, therefore I would let the figures unchanged

{\color{red} I do not know what is the legend of figure 5.  However, if all four modeled concepts are virtual models, their graphical representation should be the same. I find the same problem with figure 3. As a matter of fact all models from Figure 2, 3 and 5 use various representations and one wonders when it is UML, when it is a conceptual model?}Based on this approach, we organize our set of models following the
architecture of the aforementioned Fig.~\ref{fig:MultilevelArchitecture}. The
resulting multi-level architecture is organized in two virtual models, one
defining the core concepts metamodel including the definition of Processes and
Tasks, and one, the Acme metamodel, extending the previous model to specialize
the Acme definitions. The \FML language defines multiple inheritance concept
between virtual models as illustrated in the Sect.~\ref{sec:AcmeSoftwareDevelopmentProcess}.

>>>>

%{\color{red} I do not know what is the legend of figure 5.  However, if all
%  four modeled concepts are virtual models, their graphical representation
%  should be the same. I find the same problem with figure 3. As a matter of
%  fact all models from Figure 2, 3 and 5 use various representations and one
%  wonders when it is UML, when it is a conceptual model?}{\color{pink} (JC) we
%  discussed the reprenstation during the writing and agreed on the current
%version. Reviewers did not seem to be lost, therefore I would let the figures
%unchanged}

Based on this approach, we organize our set of models following the
architecture of the aforementioned Fig.~\ref{fig:MultilevelArchitecture}. The
resulting multi-level architecture is organized in two virtual models, one
defining the core concepts metamodel including the definition of Processes and
Tasks, and one, the Acme metamodel, extending the previous model to specialize
the Acme definitions. The \FML language defines multiple inheritance concept
between virtual models as illustrated in the Sect.~\ref{sec:AcmeSoftwareDevelopmentProcess}.
